Planetary perturbers: Flaring star-planet interactions in Kepler and TESS

### 2023-10-06 src/tex/ms.tex
[showyourwork] overleaf sync

\textcolor{red}{Here, we assume that the magnetopause radius extends to where the magnetic pressures of planet and stellar magnetic wind -- which is dominated by the magnetic field in de sub-Alf\'enic regime -- are equal. We also replace the stellar wind density $\rho_W$ with its proportionality to $\rho_* (R_* / a)^{2}$, and stellar wind magnetic field at the planetary radius $B_W$ with the surface field strength $B_* (R_* / a)^{3}$, which result in the total $R_*^2 a^{-2}$ factor in the above equation. Since the stellar wind density at the stellar surface $\rho_*$ is poorly constrained empirically~\citep{vidotto2021evolution}, we follow~\citet{alvarado-gomez2020tuning,kavanagh2021planetinduced}, and fix $\rho_*=2\cdot10^{-10}\rm{cm}^{-3}$. The angle between the wind magnetic field vector and the velocity vector of the planet $\theta$ is also unknown, so we set $\sin\theta=1$ to obtain an upper limit. In reality, $\theta$ will vary both between systems, and over time in any individual system. Omitting $\rho_*$ assumes that all stellar wind densities are the same in our sample, which is not true in reality. The dependence on $\rho_*$ is stronger than that on $B_*$, but weaker than on every other parameter, so it may dominate the magnetic field dependence.}

@@

\begin{table}
\movetableright=-10mm
\script{paper_aumic_table.py}
\caption{\textcolor{red}{Powers of star-planet interaction calculated for AU Mic in the four different scenarios introduced in Section~\ref{sec:methods:pspi}.}}
\input{output/aumic_spi.tex}
    \label{tab:aumic}
\end{table}

>>>>

\textcolor{red}{Here, we assume that the magnetopause radius extends to where the magnetic pressures of planet and stellar magnetic wind -- which is dominated by the magnetic field in de sub-Alf\'enic regime -- are equal. We also replace the stellar wind density $\rho_W$ with its proportionality to $\rho_* (R_* / a)^{2}$, and stellar wind magnetic field at the planetary radius $B_W$ with the surface field strength $B_* (R_* / a)^{3}$, which result in the total $R_*^2 a^{-2}$ factor in the above equation. Since the stellar wind density at the stellar surface $\rho_*$ is poorly constrained empirically~\citep{vidotto2021evolution}, we follow~\citet{alvarado-gomez2020tuning,kavanagh2021planetinduced}, and fix $\rho_*=2\cdot10^{10}\rm{cm}^{-3}$. The angle between the wind magnetic field vector and the velocity vector of the planet $\theta$ is also unknown, so we set $\sin\theta=1$ to obtain an upper limit. In reality, $\theta$ will vary both between systems, and over time in any individual system. Omitting $\rho_*$ assumes that all stellar wind densities are the same in our sample, which is not true in reality. The dependence on $\rho_*$ is stronger than that on $B_*$, but weaker than on every other parameter, so it may dominate the magnetic field dependence.}

@@

% \begin{table}
% \movetableright=-10mm
% \script{paper_aumic_table.py}
% \caption{\textcolor{red}{Powers of star-planet interaction calculated for AU Mic in the four different scenarios introduced in Section~\ref{sec:methods:pspi}.}}
% \input{output/aumic_spi.tex}
%     \label{tab:aumic}
% \end{table}
